Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
partially revised sec 4.3

\subsection{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution given below at $I_b=16,F_b=24$,
which has all coefficients 0.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

In the first {\sc verify} phase we obtain the following counterexample:

$$
\blue{
\Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
}
$$

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\blue{
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
}
$$

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. Back in the {\sc synthesise}
phase, we thus retrieve a candidate solution with all coefficients 0.
The {\sc verify} phase now provides the first counterexample at higher
precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\blue{
\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
}
$$

@@

$$
\blue{
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
}
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

This candidate solution is validated as the final solution by the next 
{\sc verify} phase, which fails to find a new counterexample (i.e. returns UNSAT).

>>>>

\subsection{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

In the first {\sc verify} stage, the {\sc uncertainty} 
check finds the following counterexample:

$$
\Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
$$

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
$$

This time the {\sc uncertainty} check doesn't find any more counterexamples 
and we pass the current candidate solution to the {\sc precision} verification stage.
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
We obtain the result $false$, meaning that the current precision is insuficient.
Consequently, we increase our precision to $I_b=20,F_b=28$.
%
Since the previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. Back in the {\sc synthesise}
phase, we re-start the process with a candidate solution with all coefficients 0.
Next, the {\sc uncertainty} verification stage provides the first counterexample at higher
precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
$$

@@

$$
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

This candidate solution is validated as the final solution by both stages 
{\sc uncertainty} and {\sc precision} in the
{\sc verify} phase. %, which fails to find a new counterexample (i.e. returns UNSAT).
